### 2019-08-31 Writeup/Paper/sections/abstract.tex
Changes; - Implemented corrections for the paper

\emph{Abstract} -- Many encrypted connections require the comparison of a fingerprint to
protect against eavesdropping. A substantial amount of past work has
aimed to propose fingerprint representations that work better with hu-
man limitations. ``Trustwords'' proposed by pEp is an example of such a
scheme, where the fingerprint is encoded as words in an attempt to improve
usability.
\\\\
This works main aim is to assess if Trustword’s recommended minimum
number of four words is sufficient. In order to achieve this goal, this work
implements an attack on Trustwords and quantifies its effectiveness on
more than 400 participants. A tool called GreenOnion was designed to
assist in quantifying attack feasibility. GreenOnion improved substantially
on a similar tool’s ability to search for matches concurrently where it was
able to search for over 1.5 million concurrent keys. Our findings show a
substantial increase in attack success compared to related literature. We
believe this increase is due to levering the design flaws in the Trustword
scheme. Therefore, we believe a minimum of four Trustwords is insufficient
to provide even a basic level of security.

>>>>

\emph{Abstract} -- Many encrypted connections require the comparison of a fingerprint to
protect against eavesdropping. A substantial amount of past work has
aimed to propose fingerprint representations that work better with human limitations. ``Trustwords'' proposed by pEp is an example of such a
scheme, where the fingerprint is encoded as words in an attempt to improve
usability.
\\\\
This work's main aim is to assess if Trustword’s recommended minimum
number of four words is sufficient. In order to achieve this goal, this work
implements an attack on Trustwords and quantifies its effectiveness on
more than 400 participants. A tool called GreenOnion was designed to
assist in quantifying attack feasibility. GreenOnion improved substantially
on a similar tool’s ability to search for matches concurrently. Our findings show a
substantial increase in attack success compared to related literature. We
believe this increase is due to levering the design flaws in the Trustword
scheme. Therefore, we believe a minimum of four Trustwords is insufficient
to provide even a basic level of security.

### 2019-08-31 Writeup/Paper/sections/background.tex
Changes; - Implemented corrections for the paper

An E2EE connection uses the key types discussed previously to ex-
change messages between verified parties securely. However, this hinges
on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is
completely circumvented. Therefore, the correct identification of parties is crucial to maintaining security. The exploitation of this is known as a Man-in-the-middle (MiTM) attack. This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience.

@@

\textbf{Soundex} - One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.  Soundex is one of the most famous example of a phonetic. This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.

\textbf{NYSIIS} - The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for the phonetic matching of American names. The motivation for its inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).

@@

\textbf{Phonetic Vectors} - Phonetic Vectors is a unique addition to the chosen set. Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word. Phonetic features are used in this work as a way to compare the similarity of phonemes. Phonemes are the phonetic elements that construct a word. For example, the word ``RING" translated into the phonemes \verb|/R IH NG/|.

>>>>

An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely. However, this hinges
on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is
completely circumvented. Therefore, the correct identification of parties is crucial to maintaining security. The exploitation of this is known as a Man-in-the-middle (MiTM) attack. This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience.

@@

\textbf{Soundex} - One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.  Soundex is one of the most famous example of a phonetic algorithm. This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.

\textbf{NYSIIS} - The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for the phonetic matching of American names. The motivation for its inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with). It was in use right up until the end of 1998 within various US Government departments.

@@

\textbf{Phonetic Vectors} - Phonetic Vectors; created by Allison Parrish in 2017\cite{parrish2017poetic}, is as the name suggests the vectorisation of the phonetics of a word. Phonetic features are used in this work as a way to compare the similarity of phonemes. Phonemes are the phonetic elements that construct a word. For example, the word ``RING" translated into the phonemes \verb|/R IH NG/|.

### 2019-08-31 Writeup/Paper/sections/design.tex
Changes; - Implemented corrections for the paper

\subsection{Attack Design}
\label{sec:attackDesign}
The propossed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
\\\\
As each combined key in Trustwords is an exclusive-or of both sides' public-key, therefore, the attack is designed to target a single pair of users and requires recomputation for each attack target pair. Each pair is split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered. The Controlled key is the one we are attempting to impersonate. It is assumed that there is the ability to replace the Controlled key with the malicious option. The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication. This, however, requires performing the attack twice.
\\\\
When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint. Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches. This aspect of using an extensive list to search for keys massively reduces the complexity of the search.

@@

    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision key fingerprints.

    \item Use a list of near-collision keys in the mass computation of keys to find near-collision keys.

@@

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target key fingerprints. This list is then used as a search criterion when searching for keys. To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework. OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.

>>>>

\subsection{Attack Design}
\label{sec:attackDesign}
The propossed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
\\\\
The attack is designed to target a single pair of users and requires recomputation for each attack target pair. Each pair is split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered. The Controlled key is the one we are attempting to impersonate. It is assumed that there is the ability to replace the Controlled key with the malicious option. The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication.
\\\\
When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint. Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches. This aspect of using an extensive list to search for keys massively reduces the complexity of the search.

@@

    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision fingerprints.

    \item Use a list of near-collision fingerprints in the mass computation of keys to find near-collision keys.

@@

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target key fingerprints. This list is then used as a search criterion when searching for keys. To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework. OpenCL allows the creation of code chunks referred to as ``kernels'' to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.

### 2019-08-31 Writeup/Paper/sections/discussion.tex
Changes; - Implemented corrections for the paper

\subsection*{Similar metrics performance}
Another area of further work is the comprehensive assessment of algorithms used to assess phonetic similarity. The algorithms assessed in this work are a very small proportion of potential options. Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models. A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased number of metrics. Other elements for consideration could be age, location and dialect as variables that affect a metrics performance.

\subsection*{GreenOnion optimizations}
A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could improve the performance of the attack and allow for more effective keys to be computed in less time.

>>>>

\subsection*{Similar metrics performance}
Another area of further work is the comprehensive assessment of algorithms used to assess phonetic similarity. The algorithms assessed in this work are a very small proportion of potential options. Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models. A conclusion could be reached by re-running the experiment with an increased number of metrics. Other elements for consideration could be age, location and dialect as variables that affect a metrics performance.

\subsection*{GreenOnion optimisations}
A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could improve the performance of the attack and allow for more effective keys to be computed in less time.

### 2019-08-31 Writeup/Paper/sections/experimental_design.tex
Changes; - Implemented corrections for the paper

\subsection{Metric performance}
This experiment aims to reduce the number of metrics to assess in the later rounds. The thinning out of metrics is required due to limited resources. Therefore, possible further work could involve repeating this work with a much more varied selection of metrics. The chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
\\\\
The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).

@@

The first was the addition of five "Random matches" questions. These are matches consisting of two random words selected from the dictionary. Therefore, the expected average rating of these words should be close to one. This design allows for a simple check for valid results. If their average rating for Random matches is too high, their results are discarded.

Alongside this, was the addition of two questions comparing precisely the same word. As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded. Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.

\begin{figure}[h!]
    \centering
    \begin{adjustbox}{width=0.5\textwidth,center}
        \fbox{
            \includegraphics[width=\textwidth]{experiment/exact_experiment_match.png}
        }
    \end{adjustbox}
    \caption{Exact experiment attention question}
    \label{fig:exactMatch}
\end{figure}

@@

\subsection{Trustword Attacks}
\label{sec:exp2_design}

@@

\subsubsection{Design}

@@

The start and ends were chosen as the highest priority words to keep static. This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.

@@

% \begin{table}[h!]
%     \centering
%     \input{tables/design/attack_types.tex}
%     \caption{Summary of attack requirements}
%     \label{tab:attackReq}
% \end{table}

@@

\subsubsection{Quality control}
\label{sec:exp2_quality}
Like the previous experiment, participants are sourced from MTurk. Therefore, again, quality control is an aspect that requires consideration. As with the previous study, initially screened native speakers are used. Alongside this, two metrics are used to detect invalid results: audio-button-clicks and the overall-time.

Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:trustwordUI} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to allow non-clicks. This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

Overall-time is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses. A benchmark for the time is set by completing the experiment as fast as possible. Anything quicker was discarded as anything faster risks invalid and rushed results.

>>>>

\subsection{Experiment 1 - Metric performance}
This experiment aims to reduce the number of metrics to assess in the later rounds. The thinning out of metrics is required due to limited resources. Therefore, possible further work could involve repeating this work with a much more varied selection of metrics. The chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors (See Section \ref{sec:similarity_metric}).
\\\\
The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).

@@

The first was the addition of five ``Random matches" questions. These are matches consisting of two random words selected from the dictionary. Therefore, the expected average rating of these words should be close to one. This design allows for a simple check for valid results. If their average rating for Random matches is too high, their results are discarded.

Alongside this, was the addition of two questions comparing precisely the same word. As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.

@@

\subsection{Experiment 2 - Trustword Attacks}
\label{sec:exp2_design}

@@

\subsubsection*{Design}

@@

@@

\begin{table}[h!]
    \centering
    \begin{adjustbox}{width=0.5\textwidth,center}
        \input{tables/design/attack_types.tex}
    \end{adjustbox}
    \caption{Summary of attack requirements}
    \label{tab:attackReq}
\end{table}

@@

\subsubsection*{Quality control}
\label{sec:exp2_quality}
Like the previous experiment, participants are sourced from MTurk. Therefore, again, quality control is an aspect that requires consideration. As with the previous study, initially screened native speakers are used. Alongside this, two metrics are used to detect invalid results: \textit{audio-button-clicks} and the \textit{overall-time}.

\textbf{Audio-buttons-clicks} is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:trustwordUI} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to allow non-clicks. This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

\textbf{Overall-time} is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses. A benchmark for the time is set by completing the experiment as fast as possible. Anything quicker was discarded as anything faster risks invalid and rushed results.

### 2019-08-31 Writeup/Paper/sections/introduction.tex
Changes; - Implemented corrections for the paper

One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) ``Trustwords''. Trustwords is an implementation of word fingerprint mapping with a emphasis on usability. This increase in usability is achieved by the user comparing a reduced number of words. This usability boost, however, comes at a cost of a much larger word list ($2^{16}$ words).

>>>>

One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) ``Trustwords''. Trustwords is an implementation of word fingerprint mapping with a emphasis on usability. This claimed increase in usability is achieved by the user comparing a reduced number of words. The intended usability boost, however, comes at a cost of a much larger word list ($2^{16}$ words).

### 2019-08-31 Writeup/Paper/sections/results.tex
Changes; - Implemented corrections for the paper

Figure \ref{tab:exp1_results} shows the average results for the selected matches.. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.

@@

\section{Experiment 2 - Trustword attacks}

\begin{table*}[t]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|ll|l|l|l|}
            \hline
            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
            \hline
            Levenshtein && 218 & 1101 & 19.8\% \\
            \hline
            & \OOOO   & 34  & 358  & ~~9.5\% \\
            & \XOOO   & 59  & 353  & 16.7\% \\
            & \XOOX   & 125  & 390  & 32.1\% \\
            \hline\hline
            Metaphone &&  181 & 1072 & 16.9\% \\
            \hline
            & \OOOO   & 38 & 345 & 11.0\% \\
            & \XOOO   & 57 & 375 & 15.2\% \\
            & \XOOX   & 86 & 352 & 24.4\% \\
            \hline\hline
            NYSIIS &&  209 & 1114 & 18.8\% \\
            \hline
            & \OOOO   & 36 & 385 & ~~9.3\% \\
            & \XOOO   & 72 & 375 & 19.2\% \\
            & \XOOX   & 101 & 354 & 28.5\% \\
            \hline\hline
            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table*}

>>>>

Figure \ref{tab:exp1_results} shows the average results for the selected matches. It can be seen that Levenshtein came out substantially above the rest. Levenshtein also has a much more significant proportion of 4 and 5 ratings than the alternatives.

@@

\subsection{Experiment 2 - Trustword attacks}

\begin{table*}[t]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|ll|l|l|l|}
            \hline
            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
            \hline
            Levenshtein && 218 & 1101 & 19.8\% \\
            \hline
            & \OOOO   & 34  & 358  & ~~9.5\% \\
            & \XOOO   & 59  & 353  & 16.7\% \\
            & \XOOX   & 125  & 390  & 32.1\% \\
            \hline\hline
            NYSIIS &&  209 & 1114 & 18.8\% \\
            \hline
            & \OOOO   & 36 & 385 & ~~9.3\% \\
            & \XOOO   & 72 & 375 & 19.2\% \\
            & \XOOX   & 101 & 354 & 28.5\% \\
            \hline\hline
            Metaphone &&  181 & 1072 & 16.9\% \\
            \hline
            & \OOOO   & 38 & 345 & 11.0\% \\
            & \XOOO   & 57 & 375 & 15.2\% \\
            & \XOOX   & 86 & 352 & 24.4\% \\
            \hline\hline
            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table*}

### 2019-08-31 Writeup/Thesis/chapters/evaluation.tex
Changes; - Implemented corrections for the paper

\subsection*{GreenOnion optimizations}
A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could improve the performance of the attack and allow for more effective keys to be computed in less time.

>>>>

\subsection*{GreenOnion optimisations}
A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could improve the performance of the attack and allow for more effective keys to be computed in less time.
